---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

dataset: column 8-26: selected features
column 27+: from PCA

```{r}
trainDat = read.csv('train_engineered_new.csv', header = TRUE)
testDat = read.csv('test_engineered_new.csv', header = TRUE)
trainDat$interest_level <- as.character(trainDat$interest_level)
trainDat
```

# delete outliers

skewness for continous columns
```{r}
library(e1071)   
for(i in 2:5){
  print(skewness(trainDat[,i]))}
print(skewness(trainDat[,44])) # price
```

minmax scaler for latitude longitude price (continuous variable)
```{r}

train_min <- as.numeric(apply(trainDat, 2, min))
train_max <- as.numeric(apply(trainDat, 2, max))

for (i in c(4,5,44)) {
  trainDat[, i] <- (trainDat[, i] - train_min[i]) / (train_max[i] - train_min[i]) 
  # use the min and max from training data to normalize the testing data
  testDat[, i] <- (testDat[, i] - train_min[i]) / (train_max[i] - train_min[i]) 
}

```

```{r}
boxplot(trainDat[,c(4,5,44)])
```

# looks like each column has outliers

```{r}
# save for text analysis
trainDat[(trainDat$latitude<0.85 | trainDat$longitude > 0.5 | trainDat$longitude < 0.3 | trainDat$price > 0.08), ]
```
delete 2541, 4685, 6174, 7707th row for text analysis

```{r}
trainDat <- trainDat[!(trainDat$latitude<0.85 | trainDat$longitude > 0.5 | trainDat$longitude < 0.3 | trainDat$price > 0.08), ]
```

```{r}
boxplot(trainDat[,c(4,5,44)])
```



```{r}
for(i in c(4,5,44)){
  print(skewness(trainDat[,i]))}
```

```{r}
# scatter plot
library(ggplot2)
sp2<-ggplot(trainDat, aes(x=latitude, y=longitude, color=interest_level)) + geom_point()
sp2
```

train_min <- as.numeric(apply(trainDat, 2, min))
train_max <- as.numeric(apply(trainDat, 2, max))

for (i in c(4,5,44)) {
  trainDat[, i] <- (trainDat[, i] - train_min[i]) / (train_max[i] - train_min[i]) 
  # use the min and max from training data to normalize the testing data
  testDat[, i] <- (testDat[, i] - train_min[i]) / (train_max[i] - train_min[i]) 
}



# looks like better

Now, 7th column is street_address that still not cleanned.
the street_address has only last word has some meaning(street, ave, St., Avenue, Ave, ...) We can use RNN deep learning model to detect it. For now, just delete it.

Now the data is cleanned and we can use all attributes. 

#Select important features

#feature importance

rpart
#https://stackoverflow.com/questions/21029019/parallel-execution-of-train-in-caret-fails-with-function-not-found parallel option

```{r}
library(caret)
set.seed(100)
trainDat_copy <- trainDat
trainDat_copy$interest_level <- as.character(trainDat_copy$interest_level)
rPartMod <- train(interest_level ~ ., data = trainDat_copy, method = "rpart")
#family = "multinomial"

```

```{r}
rpartImp <- varImp(rPartMod)
print(rpartImp)
```

choose these features: price + no.fee	+ hardwood + dishwasher + X1 + longitude

```{r}
# random forest
set.seed(100)
trainDat_copy <- trainDat
trainDat_copy$interest_level <- as.character(trainDat_copy$interest_level)
rfMod <- train(interest_level ~ ., data = trainDat_copy, method = "rf")
```
```{r}
rfImp <- varImp(rfMod)
print(rfImp)
```

Boruta
https://www.datacamp.com/community/tutorials/feature-selection-R-boruta?utm_source=adwords_ppc&utm_campaignid=898687156&utm_adgroupid=48947256715&utm_device=c&utm_keyword=&utm_matchtype=b&utm_network=g&utm_adpostion=&utm_creative=229765585183&utm_targetid=aud-299261629574:dsa-429603003980&utm_loc_interest_ms=&utm_loc_physical_ms=9000712&gclid=Cj0KCQjwgtWDBhDZARIsADEKwgPb0dd8xS7FCzwB5cb2uW-ImaZJvOgPKwoOLGYCNzi-ci-QEfn9hM4aAjXQEALw_wcB

https://www.youtube.com/watch?v=VEBax2WMbEA

```{r}
library(Boruta)
set.seed(1)
boruta = Boruta(factor(interest_level) ~ ., data = trainDat_copy, doTrace = 2, maxRuns = 50)
print(boruta)
plotImpHistory(boruta)
getNonRejectedFormula(boruta)
```

3 tentative attributes left: garden.patio, live.in.super, parking.space;
factor(interest_level) ~ bathrooms + bedrooms + latitude + longitude + 
    balcony + cats.allowed + common.outdoor.space + dining.room + 
    dishwasher + dogs.allowed + doorman + elevator + exclusive + 
    fitness.center + furnished + garage + garden.patio + hardwood + 
    high.ceilings + high.speed.internet + laundry.in.building + 
    laundry.in.unit + laundry.room + live.in.super + loft + lowrise + 
    new.construction + no.fee + outdoor.space + parking.space + 
    pre.war + private.outdoor.space + reduced.fee + renovated + 
    roof.deck + simplex + X0 + X1 + X2 + price

X0, X1, X2 are from PCA. I deleted them later.

# final selected features

```{r}
columns <- 'price + no.fee	+ hardwood + dishwasher + X1 + longitude +  bathrooms + bedrooms + latitude + longitude + balcony + cats.allowed + common.outdoor.space + dining.room +     dishwasher + dogs.allowed + doorman + elevator + exclusive +  fitness.center + furnished + garage + garden.patio + hardwood +     high.ceilings + high.speed.internet + laundry.in.building +     laundry.in.unit + laundry.room + live.in.super + loft + lowrise +     new.construction + no.fee + outdoor.space + parking.space +     pre.war + private.outdoor.space + reduced.fee + renovated +     roof.deck + simplex + X0 + X1 + X2 + price'
col_result <- unique(unlist(strsplit(columns, "\\+")))
coef <- capture.output(cat(col_result, sep = '+'))
coef

```

formula: price + no.fee + hardwood + dishwasher + X1 + longitude +  bathrooms + bedrooms + latitude + balcony + cats.allowed + common.outdoor.space + dining.room +     dishwasher + dogs.allowed + doorman + elevator + exclusive +  fitness.center + furnished + garage + garden.patio +     high.ceilings + high.speed.internet + laundry.in.building +     laundry.in.unit + laundry.room + live.in.super + loft + lowrise +     new.construction + no.fee + outdoor.space + parking.space +     pre.war + private.outdoor.space + reduced.fee + renovated +     roof.deck + simplex + X0 + X2 + price

```{r}
#use this one

trainDat$interest_level <- as.numeric(trainDat$interest_level)
library(caret)
dummies <- dummyVars(formula = ~ interest_level + price + no.fee + hardwood + dishwasher + X1 + longitude +  bathrooms + bedrooms + latitude + balcony + cats.allowed + common.outdoor.space + dining.room +     dishwasher + dogs.allowed + doorman + elevator + exclusive +  fitness.center + furnished + garage + garden.patio +     high.ceilings + high.speed.internet + laundry.in.building +     laundry.in.unit + laundry.room + live.in.super + loft + lowrise +     new.construction + no.fee + outdoor.space + parking.space +     pre.war + private.outdoor.space + reduced.fee + renovated +     roof.deck + simplex + X0 + X2 + price, data = trainDat)
train_dummies = predict(dummies, newdata = trainDat)
write.csv(train_dummies, file = 'feature_selection_dummies_0417.csv', row.names = FALSE)

dummies <- dummyVars(formula = ~ price + no.fee + hardwood + dishwasher + X1 + longitude +  bathrooms + bedrooms + latitude + balcony + cats.allowed + common.outdoor.space + dining.room +     dishwasher + dogs.allowed + doorman + elevator + exclusive +  fitness.center + furnished + garage + garden.patio +     high.ceilings + high.speed.internet + laundry.in.building +     laundry.in.unit + laundry.room + live.in.super + loft + lowrise +     new.construction + no.fee + outdoor.space + parking.space +     pre.war + private.outdoor.space + reduced.fee + renovated +     roof.deck + simplex + X0 + X2 + price, data = trainDat)
test_dummies = predict(dummies, newdata = testDat)
write.csv(test_dummies, file = 'feature_selection_dummies_test_0417.csv', row.names = FALSE)
```



```{r}
train_dummies
```


```{r}
testDat
```
























